WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-09-15 ms.tex
Redo abstract

\begin{abstract}
\marginpar{Wrong emphasis? I like Larry's idea of having this paper discuss several different tiers of sky localization with increasing accuracy and latency.}%
Timely \acl{EM} follow\nobreakdashes-up of \acl{CBC} events detected by \acl{aLIGO} requires rapidly inferring the sky location from the \ac{GW} observations. Calculation of the posterior distribution of the sky location and intrinsic source parameters given the \ac{GW} strain takes hours with state\nobreakdashes-of\nobreakdashes-the\nobreakdashes-art \ac{MCMC} parameter estimation codes. By taking as the measurement not the \ac{GW} strain itself but the amplitude and \acl{TOA} of the putative signal at each detector, and by fixing the intrinsic source parameters, we have constructed a non-\ac{MCMC}, fully deterministic Bayesian parameter estimation algorithm that takes just seconds to produce sky maps of posterior probability.
\end{abstract}

>>>>

\begin{abstract}
Advanced LIGO and Virgo should begin detecting gravitational waves from binary neutron star and neutron star\nobreakdashes--black hole mergers within the next few years. These sources are also predicted to power a variety of electromagnetic transients. Because these signatures can be fast and faint, locating and observing them hinges on rapidly inferring the sky location from the gravitational wave observations. MCMC methods for gravitational\nobreakdashes-wave parameter estimation can take hours or more. We describe a new, non-MCMC, fully deterministic Bayesian parameter estimation algorithm that takes just seconds to produce probability sky maps that are nearly as accurate.
\end{abstract}
